Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-31 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Move timestamp message to separate code chunk

@@

```{r, GWAS1-sb, results="hide", message=FALSE}
resfile <- paste0(resdir, "bmi_summarizedBenchmark_",
                  nrow(bmi), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  sb <- bd %>% buildBench(data=bmi, ftCols = "ind_covariate",
                          parallel=TRUE, BPPARAM=multicoreParam)
  metadata(sb)$data_download_link <- "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  save(sb, file=resfile)
  duration <- round((proc.time()-t1)[3]/60,1)
}else{
  load(resfile)
}
```

This step took `r duration` minutes for `r nrow(bmi)` SNPs using `r cores` cores.

@@

```{r, GWAS1-metrics}
# rename assay to qvalue
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)

head(assay(sb))
head(colData(sb))
sb@performanceMetrics[[1]]
```

>>>>

Here we look to see if the covariate does indeed look informative.

@@

```{r, GWAS1-sb, results="hide", message=FALSE}
resfile <- paste0(resdir, "bmi_summarizedBenchmark_",
                  nrow(bmi), ".RData")
duration <- NA
if (!file.exists(resfile)){
  t1 <- proc.time()
  sb <- bd %>% buildBench(data=bmi, ftCols = "ind_covariate",
                          parallel=TRUE, BPPARAM=multicoreParam)
  metadata(sb)$data_download_link <- "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  save(sb, file=resfile)
  duration <- round((proc.time()-t1)[3]/60,1)
}else{
  load(resfile)
}
```

```{r, echo=FALSE}
if(!is.na(duration)){
  message("This step took ", duration, " minutes for ", nrow(bmi), " SNPs using ",
        cores, " cores.")
}
```

@@

```{r, GWAS1-metrics}
# rename assay to qvalue
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```
